\documentclass[a4paper]{article}

\usepackage[utf8]{inputenc}

\title{Description-Oriented Community Detection using Exhaustive Subgroup Discovery}

\date{Summarised by Laura Rodríguez Navas \vskip 0.35cm January 9, 2020}
\author{Martin Atzmueller, Stephan Doerfel, Folke Mitzlaff}

\begin{document}
	
\maketitle

\section*{The main contribution of the article}
This article is focuses on the description-oriented community detection, using exhaustive subgroup discovery to provide an structurally valid and interpretable description for communities (i. e., a set of nodes), with a graph's structures and descriptive features of a graph’s nodes. In addition, presents the COMODO algorithm that use an efficient branch and bound method with appropriate pruning techniques to provide the exhaustive subgroup discovery. The article as well shows an implementation of COMODO's algorithm that is evaluated by a selectable community quality measure using five real world datasets, and analysed the results.
\vskip 0.35cm

As a personal opinion, I consider the approach of this article so interesting and introduces an innovation because can solve problems that in contrast to global approaches is usually not achieved by classical community mining methods, that consider the nodes of a network as mere strings or ids. Also the discovered algorithm it is very relevant since can easily be incorporated into practical applications and is not limited to any systems and can be applied to any kind of graph-structured data.
\vskip 0.35cm

Another thing, the evaluation of the COMODO algorithm during the experiments is also very relevant, that reveals that it is an efficient and scalable algorithm for large datasets. Thus, that is not encountered in the typical mining methods. Additionally, the results are statistically proved, which makes them more valid and significant.	

\section*{The article structures}
The article has the structure that an article should have as a general scheme: the abstract, the introduction, the methodology, the results of the investigation and the conclusion, as well as a list of references. As well includes the sections: preliminaries, related work and acknowledgements.
\vskip 0.35cm

In the structure, I found it very curious that the article had 66 references. Is the first article I read with so many references.
 
\newpage

Specifically is structured as follows: first introduce description-oriented community detection and present the COMODO algorithm. Then, summarizes basics of subgroup discovery, and provides general notions of graphs and community quality measures. After that, the article considers three standard community quality measures: The segregation index, the inverse average ODF (out degree fraction) and the local modularity.
\vskip 0.35cm

For the three standard community quality measures that there are introduced in the introduction section, I would like to comment that initially it seems to be an optional process, which would be applied after the COMODO algorithm and yet the experiments are based on these standards. Maybe, it should be described in the related work section. Because the related work section contains the main information of this article in grater detail.
\vskip 0.35cm

The remainder of the article contains the related work and provides experiments using five data sets and discusses their results in the context of the three real-world applications. Finally, concludes the article with a summary and directions for future research.
\vskip 0.35cm

Besides from what I have commented previously on the community quality measures, I think it is a well structured article. Although it is a bit long and complicated. Complicated since I have found it is difficult to read, specially the part of the experiments. Because of the number of examples and their simultaneous comparison. I think that with fewer examples it would be easer to understand and clearer.

\section*{Contents for a presentation}
If I had to prepare a presentation, the presentation will have between 10-12 transparencies and I would follow the following structure:

\begin{itemize}
	\item The first slide would contain the title of the article, my name as the presenter, and the submission date. Additionally, information could be added about the place where it will be presented and/or information about my affiliation.
	
	\item The second slide, maybe named process, would summarize the procedures, from a dataset to a graph, the application of the COMODO algorithm and finally the processing of the quality measures. 
	
	For example, in horitzontal view: Dataset $->$ Graph $->$ COMODO algorithm $->$ Quality Measures.
	
	\item The thrith slide would contain the definition of the description-oriented community detection using subgroup discovery. Basically to answer the question: How to identify a community?
	
	\item The fourth slide, maybe named example, would contain a basic example of community detection using subgroup discovery. Perhaps this example would consist of an image of a graph, where some communities would be drawn with different colours.
	
	\item In the following three transparencies, I would provide an overview on the data sets, obtained from the three different social media applications, which are used in the experiments. I not mentioned before that the social media applications datasets are: BibSonomy, delicious and last.fm.
	
	Therefore, the first transparency would refer to BibSonomy dataset. In the second slide to the dataset delicious and finally to the last.fm dataset. Each transparency would include three figures that would shown the results of the application of COMODO algorithm for each standard quality measures in the presented datasets.
	
	Each dataset contains a high number of tags, users, resources, etc. Maybe it would be good to put an extra slide to show this data, before the last slides.
	
	\item Finally, the last slides would contain a list of main conclusions in the ante-penultimate slide, another list for future work in the penultimate slide and a typical thank-you slide at the end.
\end{itemize}

\end{document}