---
documentclass: book
principal: yes
forprint: false
fontsize: 11pt
geometry: margin = 2.5cm
bibliography: library.bib
metodobib: yes
biblio-style: plainnat
csl: methods-in-ecology-and-evolution.csl
link-citations: yes
output:
  html_document: 
    toc: yes
    fig_caption: yes
  pdf_document:
    keep_tex: no
    number_sections: yes
    citation_package: natbib
    fig_caption: yes
    template: template.tex
    includes:
      before_body: portada/latex_paginatitulo_modTFMDS.tex
    latex_engine: xelatex
---

```{r global_options, include=FALSE}
options(kableExtra.latex.load_packages = FALSE)
knitr::opts_chunk$set(
  fig.path = 'figurasR/',
  echo = TRUE,
  warning = FALSE,
  message = FALSE,
  fig.pos = "H",
  fig.align = "center",
  out.width = "95%",
  cache = FALSE
) 
```

\setlength{\parindent}{1em}

\pagestyle{fancy}
\ifdefined\ifdoblecara
\fancyhead[LE,RO]{}
\fancyhead[LO,RE]{}
\else
\fancyhead[RO]{}
\fancyhead[LO]{}
\fi
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}
\pagenumbering{roman}

\setcounter{tocdepth}{4}
\subpdfbookmark{Índice General}{indice}
\tableofcontents

\cleardoublepage   

\pagenumbering{arabic}

\ifdefined\ifdoblecara
\fancyhead[LE,RO]{\scriptsize\rightmark}
\fancyfoot[LO,RE]{\scriptsize\slshape \leftmark}
\fancyfoot[C]{}
\fancyfoot[LE,RO]{\footnotesize\thepage}
\else
\fancyhead[RO]{\scriptsize\rightmark}
\fancyfoot[LO]{\scriptsize\slshape \leftmark}
\fancyfoot[C]{}
\fancyfoot[RO]{\footnotesize\thepage}
\fi

\renewcommand{\headrulewidth}{0.4pt}
\renewcommand{\footrulewidth}{0.4pt}

```{r child = 'capitulo01.Rmd'}
```

\FloatBarrier

```{r child = 'capitulo02.Rmd'}
```

\FloatBarrier

```{r child = 'capitulo03.Rmd'}
```

\FloatBarrier

```{r child = 'capitulo04.Rmd'}
```

\FloatBarrier
\cleardoublepage

\ifdefined\ifdoblecara
  \fancyhead[LE,RO]{}
  \fancyfoot[LO,RE]{}
  \fancyhead[CO,CE]{Bibliografía}
\else
  \fancyhead[RO]{}
  \fancyfoot[LO]{}
  \fancyhead[CO]{Bibliografía}
\fi

\ifdefined\ifcitapandoc

\hypertarget{bibliografuxeda}{%
\chapter*{Bibliografía}\label{bibliografuxeda}}
\addcontentsline{toc}{chapter}{Bibliografía}

\else

\nocite{Luque2017}
\nocite{Campos2018}
\nocite{Jimenez2019}
\nocite{HyndmanAthanasopoulos2018}
\nocite{HyndmanKhandakar2008}
\nocite{BoxJenkins1976}
\nocite{abd2015comparative}

\fi 
