---
title: "Practical 2: Model Evaluation"
author: "Laura Rodriguez Navas"
date: "January 2020"
output:
  html_document: default
  pdf_document: default
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

### Question 1
Load the data into R. Name the columns to better identify the board, as visited from left to right and from top to down.

```{r}
data <- read.table("tic-tac-toe.data.txt", header=FALSE, sep=",")
names(data) <- c("top-left-square", 
                 "top-middle-square", 
                 "top-right-square", 
                 "middle-left-square", 
                 "middle-middle-square", 
                 "middle-right-square", 
                 "bottom-left-square", 
                 "bottom-middle-square",
                 "bottom-right-square", 
                 "Class")
```

Make valid column names.

```{r}
colnames(data) <- make.names(colnames(data))
```

Check for missing values.

```{r}
any(is.na(data))
```

### Question 2
Read the "data splitting" section at the web page of caret. Then split the data into 70% training and 30% test by keeping the original proportion of classes.

```{r include=FALSE}
library(lattice)
library(ggplot2)
library(caret)
```

```{r}
set.seed(825)
inTraining <- createDataPartition(data$Class, p=.7, list=FALSE)
data_training <- data[ inTraining,]
data_testing  <- data[-inTraining,]
```

### Question 3
Specifiy the type of resampling.

```{r}
fitControl <- trainControl(method="repeatedcv", 
                           number=10, 
                           repeats=1)
```

Apply the next models to the data training dataset.

1. Model Naive Bayes

```{r include=FALSE}
library(e1071)
library(naivebayes)
```

```{r}
set.seed(825)
nb <- train(Class ~ ., 
            data=data_training, 
            method="naive_bayes",
            trControl=fitControl)
nb
```

2. Model Decision Tree

```{r include=FALSE}
library(rpart)
```

```{r}
set.seed(825)
dt <- train(Class ~ ., 
            data=data_training, 
            method="rpart2",
            trControl=fitControl)
dt
```

3. Model Neural Network

```{r include=FALSE}
library(nnet)
```

```{r}
set.seed(825)
nn <- train(Class ~ ., 
            data=data_training, 
            method="nnet",
            trControl=fitControl)
nn

```

4. Nearest Neighbour

```{r}
set.seed(825)
knn <- train(Class ~ ., 
             data=data_training, 
             method="knn",
             trControl=fitControl)
knn
```

5. Model SVM (linear kernel)

```{r include=FALSE}
library(kernlab)
```

```{r}
set.seed(825)
svm <- train(Class ~ ., 
             data=data_training, 
             method="svmLinear",
             trControl=fitControl)
svm
```

Collect the resampling results for all the models.

```{r}
resamps <- resamples(list("Naive Bayes"=nb,
                          "Decision Tree"=dt,
                          "Neural Network"=nn,
                          "Nearest Neighbour"=knn,
                          "SVM (linear kernel)" = svm))
summary(resamps)
```

Complete the following table with the final values of accuracy and kappa for the training data:

### Question 4
Apply the next models to the data test dataset.