---
title: "Practical 2: Model Evaluation"
author: "Laura Rodriguez Navas"
date: "January 2020"
output:
  pdf_document: 
    fig_caption: yes
    keep_tex: yes
  html_document: 
    df_print: default
    fig_caption: yes
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Question 1
Load the data into R. Name the columns to better identify the board, as visited from left to right and from top to down.

```{r}
data <- read.table("tic-tac-toe.data.txt", header=FALSE, sep=",")
names(data) <- c("top-left-square", 
                 "top-middle-square", 
                 "top-right-square", 
                 "middle-left-square", 
                 "middle-middle-square", 
                 "middle-right-square", 
                 "bottom-left-square", 
                 "bottom-middle-square",
                 "bottom-right-square", 
                 "Class")
```

```{r echo=FALSE}
colnames(data) <- make.names(colnames(data))
```

Check for missing values.

```{r}
any(is.na(data))
```

## Question 2
Read the "data splitting" section at the web page of caret. Then split the data into 70% training and 30% test by keeping the original proportion of classes.

```{r include=FALSE}
library(lattice)
library(ggplot2)
library(caret)
```

```{r}
set.seed(123)
inTraining <- createDataPartition(data$Class, p=.7, list=FALSE)
data_training <- data[ inTraining,]
data_testing  <- data[-inTraining,]
```

## Question 3
Specifiy the type of resampling.

```{r}
fitControl <- trainControl(method="repeatedcv", 
                           number=10, 
                           repeats=1,
                           classProbs=TRUE)
```

Apply the models: Naive Bayes, Decision Tree, Neural Networks, Nearest Neighbour and SVM (linear kernel) to the data training dataset using the same seed.

1. Model Naive Bayes

```{r include=FALSE}
library(e1071)
library(naivebayes)
```

```{r}
set.seed(123)
nb <- train(Class ~ ., 
            data=data_training, 
            method="naive_bayes",
            trControl=fitControl)
```

2. Model Decision Tree

```{r include=FALSE}
library(rpart)
```

```{r}
set.seed(123)
dt <- train(Class ~ ., 
            data=data_training, 
            method="rpart2",
            trControl=fitControl)
```

3. Model Neural Network

```{r include=FALSE}
library(nnet)
```

```{r}
set.seed(123)
nn <- train(Class ~ ., 
            data=data_training, 
            method="nnet",
            trControl=fitControl)
```

4. Model Nearest Neighbour

```{r}
set.seed(123)
knn <- train(Class ~ ., 
             data=data_training, 
             method="knn",
             trControl=fitControl)
```

5. Model SVM (linear kernel)

```{r include=FALSE}
library(kernlab)
```

```{r}
set.seed(123)
svm <- train(Class ~ ., 
             data=data_training, 
             method="svmLinear",
             trControl=fitControl)
```

```{r}
resamps <- resamples(list("Naive Bayes"=nb,
                          "Decision Tree"=dt,
                          "Neural Network"=nn,
                          "Nearest Neighbour"=knn,
                          "SVM (linear kernel)"=svm))
summary(resamps)