---
title: "Practical: Data Preparation"
author: "Laura Rodriguez Navas"
date: "February 2020"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Exercise 1: Inspection of data.
The “titanic.csv” file (available on the platform) contains data on the sinking of the Titanic. Copy the file in your working directory. Then, go to R and use the command:

```{r}
titanic <- read.csv("titanic.csv",header=TRUE, sep=",")
```

Show the names of the columns.

```{r}
head(titanic, 1)
```

Observe that the first column (whose name is "X") is redundant (it denotes the identifier of each in- stance) so it could be removed. To do this, use the subset command as follows (use help if needed):

```{r}
titanic <- subset(titanic, select=-X)
```

Now try the following commands:
```{r}
titanic
head(titanic)
summary(titanic)
plot(titanic)
```

Which variables are quantitative and which variables are categorical? How can we know it?

## TODO

## Exercise 2: Working with basic graphics.
Download the file “cars.csv” from the platform. This file contains information about the speed and stopping distances of cars.

```{r}
cars <- read.csv("cars.csv", header=TRUE, sep=",")
cars <- subset(cars, select=-X)
cars
```

2.1 Make a plot of the distance field in terms of the speed field (use the $ syntax).

```{r}
plot(cars$dist, cars$speed, main="CARS", col.main = "blue", xlab="Distance", ylab="Speed")
```

2.2 Make a histogram of the distance variable.

```{r}
hist(cars$dist, main="Histogram of CARS distance", col.main = "blue", xlab="Distance", col="red")
```

2.3 Make a histogram of the speed variable.

```{r}
hist(cars$speed, main="Histogram of CARS speed", col.main = "blue", xlab="Speed", col="red")
```

The modifications of section 2.4 have been made in the previous sections.

## Exercise 3: Transformations of variables and datasets.
Now, assume that data from two more cars are made available:

# TODO

3.1 Construct a new data frame with the above data.

```{r}
new_cars <- data.frame(speed=c(21, 34), dist=c(47, 87))
new_cars
```

3.2 Add the constructed data frame to the cars data frame.

```{r}
tail(cars)
cars <- rbind(cars, new_cars)
tail(cars)
```

3.3 Sort the data in the resulting dataset by column speed (ascending).

```{r}
cars <- cars[order(cars$speed), ]
cars
```

## Exercise 4: Data manipulation.
Download the file “airquality.csv” from the platform. This dataset contains some New York air quality measurements.

```{r}
airquality <- read.csv("airquality.csv",header=TRUE, sep=",")
```

4.1 Extract the first 2 rows of the data frame and print them to the console. What does the output look like?

```{r}
head(airquality, 2)
```

4.2 How many observations (i.e. rows) are in this data frame?

```{r}
nrow(airquality)
```

4.3 What is the value of Ozone in the 40th row?

```{r}
airquality[40,1]
```

4.4 How many missing values are in the Ozone column of this data frame?

```{r}
sum(is.na(airquality$Ozone))
```

4.5 What is the mean of the Ozone column in this dataset? Exclude missing values (coded as NA) from this calculation.

```{r}
airquality_tmp <- airquality[complete.cases(airquality$Ozone), ]
sum(is.na(airquality_tmp$Ozone))
nrow(airquality_tmp)
mean(airquality_tmp$Ozone)
```

4.6 Extract the subset of rows of the data frame where Ozone values are above 31 and Temp values are above 90. What is the mean of Solar.R in this subset?

```{r}
solarSubset <- subset(airquality_tmp , airquality_tmp$Ozone > 31 | airquality_tmp$Temp > 90)
solarSubset_tmp <- solarSubset[complete.cases(solarSubset$Solar.R), ]
mean(solarSubset_tmp$Solar.R)
```

## Exercise 5: Data transformation (2).

5.1 Discretise the Ozone column into five bins (‘bin1’, ‘bin2’, ...) of equal width and a sixth bin (‘binNA’) for NA.
5.2 Discretise the Solar column into four bins of equal size and a fifth bin for NA.
5.3 Create a new column AbsDay from the columns Month and Day such that counts the number of days passed from Month=5 and
Day=1.

## Exercise 6: Data transformation (3).

## Exercise 7: Data selection.

7.1 Calculate a correlation matrix for the air dataset. Do you see a pair of attributes that are redundant?

```{r}
cor(airquality)
```

7.2 Calculate a correlation matrix for the cars dataset. Do you see a pair of attributes that are redundant?

```{r}
cor(cars)
```

7.3 Using the data frame airquality, perform a simple random sampling of 50 examples.
```{r include=FALSE}
library(dplyr)
library(tidyr)
options(tibble.print_max = Inf)
```

```{r}
sample_n(airquality, 50)
```

7.4 Using the data frame airquality, perform a stratified random sampling of 5 examples of each month.

```{r}
set.seed(1)
airquality %>%
    group_by (Month) %>%
    sample_n(., 5)
```

