---
title: "Bag of Words -> Stack (KNN + Tree + Lasso)"
author: "Sambit Mukherjee"
output:
  pdf_document:
    toc: yes
  html_document:
    number_sections: yes
    toc: yes
    theme: cosmo
    highlight: haddock
    code_folding: show
---

---

Let's import some packages for data wrangling, visualisation, text mining and machine learning.
```{r message=FALSE}
library(dplyr)
library(ggplot2)
library(tm)
library(caret)
library(rpart)
library(glmnet)
library(MASS)
```

---

# Data Import & Target Visualisation

Let's read in the training set and examine its structure.
```{r}
train <- read.csv("train.csv", stringsAsFactors = FALSE)

str(train)
```

Next, let's read in the test set and examine its structure.
```{r}
test <- read.csv("test.csv", stringsAsFactors = FALSE)

str(test)
```

Distribution of the `target` variable:
```{r}
ggplot(train) + 
  geom_bar(aes(x = target), fill = "darkblue") + 
  scale_x_continuous(breaks = c(0, 1))
```

The distribution isn't very skewed.

---

# Text Preprocessing

## Variable: `keyword`

```{r include=FALSE}
options(max.print = 250)
```

Let's examine the unique values of `keyword` in `train`.
```{r}
unique(train$keyword)
```

There are `222` unique values.

Next, let's examine the unique values of `keyword` in `test`.
```{r}
unique(test$keyword)
```

These are the same `222` unique values that are present in `train`. This makes it convenient to deal with this variable.

> **Strategy:** Simply convert `keyword` to a categorical variable.

```{r}
train$keyword <- as.factor(train$keyword)
test$keyword <- as.factor(test$keyword)
```

Let's verify that the factor levels of `keyword` in `train` and `test` match.
```{r}
all.equal(levels(train$keyword), levels(test$keyword))
```

## Variable: `location`

```{r include=FALSE}
options(max.print = 100)
```

Let's examine the unique values of `location` in `train`.
```{r}
unique(train$location)
```

There are `3342` unique values:
```{r}
length(unique(train$location))
```

Next, let's examine the unique values of `location` in `test`.
```{r}
unique(test$location)
```

There are `1603` unique values:
```{r}
length(unique(test$location))
```

We notice that the unique values of `location` in `train` and `test` aren't the same. Hence, we cannot simply convert `location` to a categorical variable.

> **Strategy:** Convert `location` to a bag of words.

### Create a corpus

Let's bind the rows of `train` and `test` (except the `target` variable) into a single data frame.
```{r}
train_and_test <- rbind(train[, 1:4], test)

str(train_and_test)
```

Next, let's create a corpus of text contained in the `location` column.
```{r}
corpus_location <- Corpus(VectorSource(train_and_test$location))
```

Let's examine it.
```{r}
corpus_location
```

It contains `10876` documents (corresponding to the `10876` rows in `train_and_test`).

Let's take a look at the 50th location.
```{r}
corpus_location[[50]]$content
```

### Convert to lowercase

```{r warning=FALSE}
corpus_location <- tm_map(corpus_location, tolower)
```

Let's see what this did to our 50th location.
```{r}
corpus_location[[50]]$content
```

### Remove punctuation

```{r warning=FALSE}
corpus_location <- tm_map(corpus_location, removePunctuation)
```

Let's see what this did to our 50th location.
```{r}
corpus_location[[50]]$content
```

### Remove stop words

```{r warning=FALSE}
corpus_location <- tm_map(corpus_location, removeWords, stopwords("english"))
```

Let's see what this did to our 50th location.
```{r}
corpus_location[[50]]$content
```

### Stem words (using Porter's stemming algorithm)

```{r warning=FALSE}
corpus_location <- tm_map(corpus_location, stemDocument)
```

Let's see what this did to our 50th location.
```{r}
corpus_location[[50]]$content
```

### Create document term matrix

```{r}
dtm_location <- DocumentTermMatrix(corpus_location)
```

Let's examine it.
```{r}
dtm_location
```

It contains `3839` terms. We notice that the matrix has an extremely high sparsity (`100%`).

### Reduce sparsity

```{r}
dtm_location <- removeSparseTerms(dtm_location, 0.9975) # Retain terms that appear in at least 0.25% of the observations.

dtm_location
```

The sparsity has reduced to `99%`. As a result, the number of terms has dropped from `3839` to `55`.

### Convert to data frame

```{r}
bag_of_words_location <- as.data.frame(as.matrix(dtm_location))
```

Let's ensure that the data frame has valid column names.
```{r}
colnames(bag_of_words_location) <- make.names(colnames(bag_of_words_location))
```

Let's also add `"_location"` to each column name to avoid any potential duplications with the `text` column's bag of words (see Section 2.3).
```{r}
colnames(bag_of_words_location) <- paste0(colnames(bag_of_words_location), "_location")
```

Finally, let's examine its structure.
```{r}
str(bag_of_words_location, list.len = 20) # Display first 20 columns.
```

## Variable: `text`

We shall preprocess the `text` column in the same manner.

> **Strategy:** Convert `text` to a bag of words.

### Create a corpus

Let's create a corpus of tweets contained in the `text` column of `train_and_test`.
```{r}
corpus_text <- Corpus(VectorSource(train_and_test$text))
```

Let's examine it.
```{r}
corpus_text
```

It contains `10876` documents (corresponding to the `10876` rows in `train_and_test`).

Let's take a look at the 1st tweet.
```{r}
corpus_text[[1]]$content
```

### Convert to lowercase

```{r warning=FALSE}
corpus_text <- tm_map(corpus_text, tolower)
```

Let's see what this did to our 1st tweet.
```{r}
corpus_text[[1]]$content
```

### Remove punctuation

```{r warning=FALSE}
corpus_text <- tm_map(corpus_text, removePunctuation)
```

Let's see what this did to our 1st tweet.
```{r}
corpus_text[[1]]$content
```

### Remove stop words

```{r warning=FALSE}
corpus_text <- tm_map(corpus_text, removeWords, stopwords("english"))
```

Let's see what this did to our first tweet.
```{r}
corpus_text[[1]]$content
```

### Stem words (using Porter's stemming algorithm)

```{r warning=FALSE}
corpus_text <- tm_map(corpus_text, stemDocument)
```

Let's see what this did to our first tweet.
```{r}
corpus_text[[1]]$content
```

### Create document term matrix

```{r}
dtm_text <- DocumentTermMatrix(corpus_text)
```

Let's examine it.
```{r}
dtm_text
```

It contains `24906` terms. We notice that the matrix has an extremely high sparsity (`100%`).

### Reduce sparsity

```{r}
dtm_text <- removeSparseTerms(dtm_text, 0.9975) # Retain terms that appear in at least 0.25% of the observations.

dtm_text
```

The sparsity has reduced to `99%`. As a result, the number of terms has dropped from `24906` to `719`.

### Convert to data frame

```{r}
bag_of_words_text <- as.data.frame(as.matrix(dtm_text))
```

Let's ensure that the data frame has valid column names.
```{r}
colnames(bag_of_words_text) <- make.names(colnames(bag_of_words_text))
```

Let's also add `"_text"` to each column name to avoid any potential duplications with the `location` column's bag of words.
```{r}
colnames(bag_of_words_text) <- paste0(colnames(bag_of_words_text), "_text")
bag_of_words_text <- bag_of_words_text[, !duplicated(colnames(bag_of_words_text))]
```

Finally, let's examine its structure.
```{r}
str(bag_of_words_text, list.len = 20) # Display first 20 columns.
```

## Putting Together

Let's bind the columns of `bag_of_words_location` and `bag_of_words_text`.
```{r}
bag_of_words <- cbind(bag_of_words_location, bag_of_words_text)
```

Next, let's separate `bag_of_words` into two data frames (for training and testing).
```{r}
train_processed <- bag_of_words[1:7613, ] # Rows 1 to 7613 were obtained from `train`.
test_processed <- bag_of_words[7614:10876, ] # Rows 7614 to 10876 were obtained from `test`.
```

Finally, let's add the `id`, `keyword` and `target` columns to `train_processed` and `test_processed`.
```{r}
train_processed$id <- train$id
train_processed$keyword <- train$keyword
train_processed$target <- train$target

test_processed$id <- test$id
test_processed$keyword <- test$keyword
```

---

# Modelling & Training Set Predictions

**Outcome variable:** `target`

**Features:**

- `keyword` (categorical variable with `222` unique values)
- All the columns obtained from `bag_of_words_location`
- All the columns obtained from `bag_of_words_text`

Since this is a classification problem, let's convert `target` to a categorical variable.
```{r}
train_processed$target <- as.factor(train_processed$target)
```

## Base Model: KNN (K Nearest Neighbours)

Let's specify 5-fold cross-validation, and define our parameter grid.
```{r}
num_folds <- trainControl(method = "cv", number = 5)
parameter_grid <- expand.grid(k = 1:5) # Explore values of `k` between 1 and 5.
```

Next, let's perform a grid search.
```{r}
grid_search <- train(
  target ~ . - id,  # Use all variables in `train_processed` except `id`.
  data = train_processed, 
  method = "knn",
  trControl = num_folds, 
  tuneGrid = parameter_grid
)

grid_search
```

The best value of `k` is `3`. Let’s use this value to train our KNN model.
```{r}
set.seed(1) # Ensure reproducibility.
knn_model <- knn3(target ~ . - id, data = train_processed, k = 3)
```

**Training set predictions:**

Let's obtain the predicted classes.
```{r}
knn_train_pred_class <- predict(knn_model, newdata = train_processed, type = "class")

summary(knn_train_pred_class)
```

**Training set confusion matrix:**
```{r}
confusionMatrix(knn_train_pred_class, train_processed$target)
```

**Training set F1 score:**
```{r}
true_positives <- 2208
false_positives <- 336
false_negatives <- 1063

precision <- true_positives / (true_positives + false_positives)
recall <- true_positives / (true_positives + false_negatives)

F1_knn <- 2 * (precision * recall) / (precision + recall)
F1_knn <- round(F1_knn, digits = 4)

F1_knn
```

## Base Model: Tree (CART)

Let's specify 5-fold cross-validation, and define our parameter grid.
```{r}
num_folds <- trainControl(method = "cv", number = 5)
parameter_grid <- expand.grid(.cp = seq(0, 0.01, 0.001)) # Explore values of `cp` between 0 and 0.01.
```

Next, let's perform a grid search.
```{r}
grid_search <- train(
  target ~ . - id, 
  data = train_processed, 
  method = "rpart", # CART algorithm
  trControl = num_folds, 
  tuneGrid = parameter_grid
)

grid_search
```

The best value of `cp` is `0`. Let’s use this value to train our tree.
```{r}
tree_model <- rpart(
  target ~ . - id,
  data = train_processed, 
  method = "class",
  cp = 0
)
```

**Variable importance:**
```{r}
tree_summary <- data.frame(
  variable = names(tree_model$variable.importance), 
  importance = tree_model$variable.importance, 
  stringsAsFactors = FALSE, 
  row.names = NULL
) %>% 
  arrange(desc(importance))

DT::datatable(tree_summary)
```

**Training set predictions:**

Let's obtain the predicted classes.
```{r}
tree_train_pred_class <- predict(tree_model, newdata = train_processed, type = "class")

summary(tree_train_pred_class)
```

**Training set confusion matrix:**
```{r}
confusionMatrix(tree_train_pred_class, train_processed$target)
```

**Training set F1 score:**
```{r}
true_positives <- 2280
false_positives <- 505
false_negatives <- 991

precision <- true_positives / (true_positives + false_positives)
recall <- true_positives / (true_positives + false_negatives)

F1_tree <- 2 * (precision * recall) / (precision + recall)
F1_tree <- round(F1_tree, digits = 4)

F1_tree
```

## Base Model: Lasso (Regularised Logistic Regression)
         
Unfortunately, the `glmnet()` function doesn't provide a formula interface. Instead, it expects an `X_train` matrix and a `y_train` vector as arguments.

The `model.matrix()` function is useful for generating `X_train`:

- It produces a matrix containing all the features.
- It automatically transforms any categorical variables (factors) into dummy variables.

Let's generate `X_train` and `y_train`.
```{r}
X_train <- model.matrix(target ~ . - id, data = train_processed)
X_train <- X_train[, 2:ncol(X_train)] # Remove the "(Intercept)" column, since `glmnet()` automatically adds an intercept.
y_train <- train_processed$target
```

Next, let's perform 5-fold cross-validation.
```{r}
set.seed(1) # Ensure reproducibility.
cross_val <- cv.glmnet(
  X_train, 
  y_train, 
  family = "binomial", # Specify logistic regression.
  alpha = 1, # Specify ridge penalty (0) or lasso penalty (1).  
  type.measure = "class", # Specify "Misclassification Error" as the loss to use for cross-validation.
  nfolds = 5
)

plot(cross_val)                              
```

The best value of `lambda` is:
```{r}
best_lambda <- cross_val$lambda.min

best_lambda
```

Let’s use this value to train our lasso model.
```{r}
lasso_model <- glmnet(X_train, y_train, family = "binomial", alpha = 1, lambda = best_lambda)
                                              
lasso_model
```

**Regression coefficients:**
```{r}
lasso_coef <- as.data.frame(as.matrix(coef(lasso_model)))
colnames(lasso_coef) <- "coefficient"

DT::datatable(lasso_coef)
```

**Training set predictions:**
                                              
Let's obtain the predicted classes.
```{r}
lasso_train_pred_class <- as.factor(predict(lasso_model, s = best_lambda, newx = X_train, type = "class"))

summary(lasso_train_pred_class)
```

**Training set confusion matrix:**
```{r}
confusionMatrix(lasso_train_pred_class, train_processed$target)
```

**Training set F1 score:**
```{r}
true_positives <- 2453
false_positives <- 403
false_negatives <- 818

precision <- true_positives / (true_positives + false_positives)
recall <- true_positives / (true_positives + false_negatives)

F1_lasso <- 2 * (precision * recall) / (precision + recall)
F1_lasso <- round(F1_lasso, digits = 4)

F1_lasso
```

## Stacking

We shall use **Quadratic Discriminant Analysis (QDA)** as our metalearner algorithm. 

Earlier, we obtained our base models' *predicted classes*. Now, let's obtain their *predicted probabilities*.
```{r}
knn_train_pred_prob <- predict(knn_model, newdata = train_processed, type = "prob")[, 2]
tree_train_pred_prob <- predict(tree_model, newdata = train_processed, type = "prob")[, 2]
lasso_train_pred_prob <- as.numeric(predict(lasso_model, s = best_lambda, newx = X_train, type = "response"))
```

Let's create the data frame for training, and examine its first `20` rows.
```{r}
stack_train <- data.frame(
  target = train_processed$target, 
  pred_knn = knn_train_pred_prob, 
  pred_tree = tree_train_pred_prob,
  pred_lasso = lasso_train_pred_prob
)

DT::datatable(head(stack_train, 20))
```

**Feature correlation matrix:**
```{r}
cor(stack_train[, 2:4])
```

The correlations are not too high. Hence, we can expect some benefit from stacking.

Now, let's train our metalearner.
```{r}
qda_model <- qda(target ~ pred_knn + pred_tree + pred_lasso, data = stack_train)

qda_model
```

**Training set predictions:**

Let's obtain the predicted classes.
```{r}
qda_train_pred_class <- predict(qda_model, newdata = stack_train)$class

summary(qda_train_pred_class)
```

**Training set confusion matrix:**
```{r}
confusionMatrix(qda_train_pred_class, train_processed$target)
```

**Training set F1 score:**
```{r}
true_positives <- 2652
false_positives <- 484
false_negatives <- 619

precision <- true_positives / (true_positives + false_positives)
recall <- true_positives / (true_positives + false_negatives)

F1_metalearner <- 2 * (precision * recall) / (precision + recall)
F1_metalearner <- round(F1_metalearner, digits = 4)

F1_metalearner
```

As expected, the metalearner has a higher F1 than the base models.

**Summary of F1 scores:**
```{r}
F1_summary <- data.frame(
  model = c("KNN", "Tree", "Lasso", "Metalearner"), 
  F1 = c(F1_knn, F1_tree, F1_lasso, F1_metalearner)
)

DT::datatable(F1_summary)
```

---

# Test Set Predictions & Submission

## Test set predictions

**KNN:**

Let's obtain the predicted probabilities.
```{r}
knn_test_pred_prob <- predict(knn_model, newdata = test_processed, type = "prob")[, 2]
```
                                              
**Tree:**

Let's obtain the predicted probabilities.
```{r}
tree_test_pred_prob <- predict(tree_model, newdata = test_processed, type = "prob")[, 2]
```

**Lasso:**

First, let's generate the `X_test` matrix using the `model.matrix()` function.
```{r}
X_test <- model.matrix(~ . - id, data = test_processed)
X_test <- X_test[, 2:ncol(X_test)] # Remove the "(Intercept)" column, since `glmnet()` automatically adds an intercept.
```
                                              
Next, let's obtain the predicted probabilities.
```{r}
lasso_test_pred_prob <- as.numeric(predict(lasso_model, s = best_lambda, newx = X_test, type = "response"))
```

**Metalearner:**

Let's put the above predictions into a data frame, and obtain the predicted classes.
```{r}
stack_test <- data.frame(
  pred_knn = knn_test_pred_prob, 
  pred_tree = tree_test_pred_prob, 
  pred_lasso = lasso_test_pred_prob
)

qda_test_pred_class <- predict(qda_model, newdata = stack_test)$class

summary(qda_test_pred_class)
```

## Submission

Let’s generate the submission dataset.
```{r}
submission <- data.frame(id = test_processed$id, target = qda_test_pred_class)
```

Finally, let's write it to disk.
```{r}
write.csv(submission, file = "submission.csv", row.names = FALSE)
```
